---
title: "Oregon Census Data"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

<style type="text/css">

.navbar-inverse .navbar-nav>.active>a, .navbar-inverse .navbar-nav>.active>a:hover, .navbar-inverse .navbar-nav>.active>a:focus {
color: #fbb034;
background-color: #00467f;
border-color: #002a4c;
font-weight: 900;
}

.chart-title {
    border-bottom: 1px solid #d7d7d7;
    color: #333333;
    font-size: 20px;
    font-weight: 700;
    padding: 7px 10px 4px;
}

.heading-level1 {  /* chart_title  */
   color: #00467f;
    font-size: 18px;
    font-weight: 500;
}

h4, .h4 {
   color: #002a4c;
    font-size: 15px;
    font-weight: 550;
}

a:visited {
   color: rgb(50%, 0%, 50%);
}

</style>

<h1>Oregon Census Visualization Example</h1>
`r format(Sys.time(), "%A, %B %d, %Y %I:%M%p ")`


```{r setup, include=FALSE}
library(flexdashboard)
library(tidycensus)
library(tidyverse)
library(tmap)
# census_api_key("", install = TRUE)
options(tigris_use_cache = T)
options(tigris_class = "sf")

```

Data Acquisition
=======================================


Column {data-width=650}
-----------------------------------------------------------------------

### ACS Variables

```{r acs variables}
v15 <- load_variables(2015, "acs5", cache = TRUE)

options("DT.warn.size" = F)

DT::datatable(v15,
              # colnames=c("Date", "Conversion Rate", "Conversations", "Bookings"),
              extensions = 'Buttons',
              rownames = FALSE,
              fillContainer = FALSE,
              autoHideNavigation = FALSE,
              options = list(dom = 'Bfrtip',
                             buttons =
                               list(
                                 # 'colvis',
                                 # 'print',
                                 list(
                                   extend = 'collection',
                                   buttons = list(list(extend='excel',
                                                       filename = 'Bookings')
                                                  # list(extend='pdf',
                                                  #      filename= 'Bookings')
                                                  ),
                                   text = 'Export'
                                 )),
                             scrollX = TRUE,
                             scrollY = "200px",
                             pageLength = 10,
                             order=list(list(1,'desc')))) %>% 
   DT::formatStyle(columns = c(3), fontSize = '50%')

```




### Load ACS health insurance coverage for Oregon

```{r load health insurance coverage, eval=FALSE}

dat12 <- get_acs(state = "OR",
                  geography = "tract", 
                  table = "B27001",
                  year = 2014,
                  cache_table = T,
                  output = "tidy",
                  geometry = TRUE) %>%
  rename(`2012` = estimate) %>%
  select(-moe)

dat16 <- get_acs(state = "OR",
                  geography = "tract", 
                  table = "B27001",
                  year = 2016,
                  cache_table = T,
                  output = "tidy",
                  geometry = TRUE) %>%
  rename(`2016` = estimate) %>%
  select(-moe)

head(dat16)

```

### 



Visualization
=======================================


References
=======================================

### Reference material

* Creating beautiful demographic maps in R with the tidycensus and tmap packages http://zevross.com/blog/2018/10/02/creating-beautiful-demographic-maps-in-r-with-the-tidycensus-and-tmap-packages/#part-2-creating-beautiful-maps-with-tmap
* Spatial data in tidycensus https://walkerke.github.io/tidycensus/articles/spatial-data.html
* Generating metropolitan subsets of Census data with R and tigris https://walkerke.github.io/2017/05/tigris-metros

### Useful commands

#### tigris rbind

```{r eval=FALSE, echo=TRUE}
orwa <- rbind_tigris(tracts("OR", cb = TRUE),  tracts("WA", cb = TRUE))
```

> https://github.com/rte-antares-rpackage/leaflet.minicharts

> Radar charts for showing attributes of different segments (median values) https://github.com/mangothecat/radarchart

> https://github.com/garthtarr/pairsD3